Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-04 minimax.tex
new logarithmic plot for linearityFig with courses xps

\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.03)},
				anchor=south
			},
		}
		\begin{axis}[
			y=3.5,
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			ytick={0,5,10,15,20,25,30,35},
			xtick distance=100,
			ytick distance=5,
			xtick pos=left,
			ymajorgrids=true,
			ytick style={draw=none},
			ymin=0,
			ymax=35,
			xmin=0,
			xmax=800,
			yticklabels={0,5,10,15,20,25,30,35}]

			\addlegendimage{mark=triangle*,teal,mark size=2}
			\addlegendimage{mark=*,violet,mark size=2}
			\addlegendimage{mark=square*,green,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}
			\addlegendimage{mark=pentagon*,cyan,mark size=2}
			\addlegendimage{mark=halfsquare*,magenta,mark size=2}

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
			\addlegendentry{m=5, n=10}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}
%\begin{figure}
%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
%
%	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
%	\includegraphics[width=.45\textwidth]{linearity.png}
%\end{figure}

>>>>

%\begin{figure}
%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
%	\label{fig:linearity}
%	\begin{tikzpicture}
%		\pgfplotsset{
%			every axis legend/.append style={
%				at={(0.5,1.03)},
%				anchor=south
%			},
%		}
%		\begin{axis}[
%			y=3.5,
%			legend columns=3,
%			xlabel=Number of Questions,
%			ylabel=Avg. Regret,
%			ytick={0,5,10,15,20,25,30,35,146},
%			xtick distance=100,
%			ytick distance=5,
%			xtick pos=left,
%			ymajorgrids=true,
%			ytick style={draw=none},
%			ymin=0,
%			ymax=146,
%			xmin=0,
%			xmax=1000,
%			yticklabels={0,5,10,15,20,25,30,35,146}]
%			
%			\addlegendimage{mark=triangle*,teal,mark size=2}
%			\addlegendimage{mark=*,violet,mark size=2}
%			\addlegendimage{mark=square*,green,mark size=2}
%			\addlegendimage{mark=diamond*,red,mark size=2}
%			\addlegendimage{mark=pentagon*,cyan,mark size=2}
%			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
%			\addlegendimage{mark=halfsquare right*,brown,mark size=2}
%			
%			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/linearity.dat};
%			\addlegendentry{m=5, n=10}
%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/linearity.dat};
%			\addlegendentry{m=5, n=15}
%			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
%			\addlegendentry{m=5, n=20}
%			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
%			\addlegendentry{m=10, n=20}
%			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
%			\addlegendentry{m=10, n=30}
%			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
%			\addlegendentry{m=15, n=30}
%			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
%			\addlegendentry{courses}
%		\end{axis}
%	\end{tikzpicture}
%\end{figure}

\begin{figure}
	\caption{Logarithmic plot representing the MMR reduction after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.03)},
				anchor=south
			},
		}
		\begin{semilogyaxis}[
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			log basis y= 10,
			ymin=10e-2,
			ymax=10e2,
			ytick={10e-2,1,2,10,15,20,30,146},
			yticklabels={0.01,1,2,10,15,20,30,146},
			ymajorgrids=true,
			ytick style={draw=none},
			xmin=0,
			xmax=1000,
			xtick={0,100,200,300,400,500,600,700,800,900,1000},
			xticklabels={0,100,200,300,400,500,600,700,800,900,1000},
			ticklabel style = {font=\tiny}
			]

			\addlegendimage{mark=triangle*,teal,mark size=2}
			\addlegendimage{mark=*,violet,mark size=2}
			\addlegendimage{mark=square*,green,mark size=2}
			\addlegendimage{mark=diamond*,red,mark size=2}
			\addlegendimage{mark=pentagon*,cyan,mark size=2}
			\addlegendimage{mark=halfsquare*,magenta,mark size=2}
			\addlegendimage{mark=halfsquare right*,brown,mark size=2}

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal, domain=-5:5] table [x=k, y=5.10]{data/linearity.dat};
			\addlegendentry{m=5, n=10}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet,domain=-5:5] table [x=k, y=5.15]{data/linearity.dat};
			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/linearity.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/linearity.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity.dat};
			\addlegendentry{m=15, n=30}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {400}, brown] table [x=k, y=courses]{data/linearity.dat};
			\addlegendentry{courses}
		\end{semilogyaxis}
	\end{tikzpicture}
\end{figure}

%\begin{figure}
%	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
%
%	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
%	\includegraphics[width=.45\textwidth]{linearity.png}
%\end{figure}
